---
title: "Linear Regression on Subsets"
output:
  html_notebook: default
  html_document: default
  pdf_document: default
---
This is an analysis on linear regression of subsets of a sample population. We want to predict the true function of a data set given a sample population. First, we create a sample dataset with the known true function and its error term.

```{r}
size = 100
min_range = 0
max_range = 100
standard_deviation = 50
slope = 2
y_int = 0

randomSampleDataSet = function (s, minr, maxr, m, y_int, sd) {
  x = runif(s, minr, maxr)
  y = x*m + rnorm(s, sd=sd) + y_int
  df = data.frame(x,y)
  return(df)
}

df = randomSampleDataSet(size, min_range, max_range, slope, y_int, standard_deviation)
plot(df)
abline(y_int, slope, col='red')
```
The sample data set is generated with the red line representing the true function. Next we fit 5 lines, each knowing 20% of the previously generated sample data set.

```{r}
number_of_fits = 5
percent_of_dataset = 0.2

createFits = function(n, pct, data){
  fits = list()
  for(i in 1:n){
    num_rows = nrow(data) * percent_of_dataset  
    randRows = data[sample(nrow(data), num_rows),] 
    fits[[i]] = lm(y ~ x, data = randRows)
  }
  return(fits)
}

plotFits = function(fits, data){
  plot(data)
  for(i in 1:length(fits)){
     abline(fits[[i]], col='blue')   
  }
}

fits = createFits(number_of_fits, percent_of_dataset, df)

plotFits(fits, df)
abline(lm(y ~ x, data = df), col="green")
abline(y_int, slope, col='red')
```